Data Analytics Introduction Using Python Training

### 2024-11-07 MsaPythonDataAnalytics.qmd
update values 1

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: false
    scrollable: true
---

@@

# Python

## Python Introduction  {.smaller}

@@

@@

## Python numpy | Introduction

@@

>>>>

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: false
    scrollable: true
code-fold: true
---

@@

# Python {.smaller}

## Python Introduction

@@

Python programming language uses it's in build command prompt frequently called *CLI* standing for *Command Line Interface*, search through windows/MAC program files and you should see *Python 3.0.0)* there are various versions of python and depending on which one you have installed this will determine the python CLI.

Though you can be able to do everything using this, it doesn't give an intuitive user interface hence the reason for development of *IDE* Integrated Development Environment.

*IDE* is the dashboard similar to car dashboard but the actual software the engine is now *python* for this case.

@@

## Python numpy | Introduction {.smaller}

***numpy***: python module/library specialized in *Arrays and Vectorized Computation*.

NumPy, short for Numerical Python, is one of the most important foundational packages for numerical computing in Python. Numpy works with array from 1-n dimenisional.

```{python}

#| echo: true

import numpy as np

my_arr = np.arange(10)

#my_list = list(range(10)) #inbuilt python

my_arr
```

Multidimensional Array

data = np.array([[1.5, -0.1, 3], [0, -3, 6.5]])

data

```

Array descriptors

data.shape
data.dtype
data.ndim

```

@@

***Pandas*** : Python module/library enhancing data manipulation tools designed to make data cleaning and analysis fast and convenient in Python. Works intandem with *numpy* and is the core working under the hood.

import pandas as pd

obj_series = pd.Series([4, 7, -5, 3])

obj_series

```

Main difference of pandas with numpy is that it has indexed values and designed for working with tabular or heterogeneous data.
